---
title: Genetic distances estimation
output:
  html_document: default
---

In this script we show the results from the estimation of genetic distances between populations on the HGDP and 1000G reference samples.
The merging of those databases can be found [here](http://tomszar.github.io/HGDP_1000G_Merge).
The first approach is to use a Nei distance on the pruned genotypes. 
The second approach is to compute a pairwise Identity-by-Descent (IBD) estimation of the full set of phased genotypes for all individuals. 
The total length of shared IBD segments between individuals (in cM) is used as a distance matrix.
Next, the total segment sharing between individuals between Population 1 and Population 2 is measured as a population-level genetic distance.

## Preliminaries

Load libraries

```{r packages, message=FALSE}
library(tidyverse)
library(heatmap3)
```

Read databases

```{r databases}
setwd('..')
path <- getwd()
setwd(paste(path, "/Results/Distances", sep = ""))
neidist <- as.matrix(read.table("Nei_dist.csv", sep=",", header=T, row.names = 1))
ibddist <- as.matrix(read.table("IBD_dist.csv", sep=",", header=T, row.names = 1))
```

## Nei's distance estimation

Heatmap from Nei's distance estimation

```{r nei heatmap, fig.height=12, fig.width=12}
heatmap(neidist, symm= T)
```

## IBD-based genetic distance

Heatmap from IBD-based genetic distance estimation

```{r heatmap IBD distance, fig.height=12, fig.width=12}
diag(ibddist) <- NA
heatmap(ibddist, symm = T)
```